---
title: "Residency Incentives"
output: html_notebook
---

# Data
``` {r}
#Source: 2016 Census
cen_pop_2016 <- 41786

#Source: https://www.fin.gov.nt.ca/sites/fin/files/2018-19_budget_address_and_papers.pdf

## Revenues
tff_1819 <- 1.256 * 10^9
all_revenue_1819 <- 1.749 * 10^9

## Expenditures
opex_1819 <- 1.713 * 10^9
ece_1819 <- 3.27 * 10^8
hss_1819 <- 4.61 * 10^8
```

# Simplifying assumptions

1. TFF is the only marginal value of a resident. This is a very conservative assumption and the residents a program would be incenting would be ones who are more likely to contribute other sources of revenue, but we'll stick with it for now.
2. Health and education are marginal costs per resident and all other government expenses are fixed costs. This is even much more untrue than assumption 1. Health and education have many fixed costs and other departments have marginal costs. However:
* it gives something of maybe a ballpark that's ok enough for now and 
* since health and education make up such a big chunk of the total expenses government's total expenses it's a very conservative ballpark.

So, I will say the following. These variables are all per capita. 
```{r}
marginal_revenue <- tff_1819 / cen_pop_2016
fixed_revenue <- all_revenue_1819 - tff_1819

marginal_cost <- (ece_1819 + hss_1819) / cen_pop_2016
fixed_cost <- opex_1819 - ece_1819 - hss_1819
```

3. The number of new residents available per year is given as a parameter; a $1 incentive spread over 10 years can still attract unlimited new residents. In fact the terms of the program, amongst many other factors, would strongly affect the success.
4. There's unlimited space for everyone.
5. Each resident immigrating or emigrating is an independent event that solely depends on the overall response-rate and exp-years-resident parameters, respectively. In fact folk would come and go in groups and in response to general events and individual circumstances and preferences.
6. No stochasticity, beyond the number of residents, to the cost or revenue. 